Supplementary Material

### 2025-05-28 manuscript/manuscript.qmd
small manuscript improvements

To model the RR interval (RRi) across a complete rest-exercise-recovery protocol, we implemented the coupled-logistic RRi-vs-time model proposed by Castillo-Aguilar et al. (2025) [@Enhancing2025Castillo]. Under this specification, each observed RRi is assumed to follow a normal distribution centered on a time-dependent function. This data generation process is depicted in @eq-data-generation-process.

@@

However, this vagal-centric profile was also characterized by a slower return to baseline heart rate after exercise. Despite a less pronounced initial increase in heart rate, individuals with more CD21^+^/CD11c^+^ B cells took longer to recover. This protracted recovery could stem from a less efficient re-establishment of autonomic balance following a moderated sympathetic response, where the sympathetic nervous system (SNS) might not have been sufficiently activated to trigger a strong subsequent vagal rebound. Alternatively, it might indicate a degree of autonomic rigidity [@Enhancing2025Castillo], where a predominantly parasympathetic system at rest exhibits difficulty in rapidly adjusting after a perturbation. The lower $c$ parameter (recovery proportion of the RRi curve) observed in this group supports the notion of reduced autonomic flexibility, suggesting that while a basal anti-inflammatory environment might be present, the capacity for rapid adaptation to acute physiological challenges could be limited.

@@

A notable and potentially beneficial finding was the excellent autonomic recovery (high $c$ parameter) observed in the CD21^-^/CD11c^-^ group despite their lower initial vagal tone. This suggests a compensatory and efficient vagal reactivation following the sympathetic surge, possibly mediated by baroreceptor and mechanoreceptor reflexes responding to the exercise-induced cardiovascular changes [@besnier2017exercise]. This efficient cholinergic recovery could aid in resolving immune activation once the exercise stimulus ceases. Thus, individuals with a more sympathicotonic profile might be capable of mounting strong but transient responses, followed by a relatively rapid return to autonomic balance mediated by the parasympathetic nervous system. This pattern resonates with descriptions of mild autonomic insufficiency, where sympathetic hyper-responsiveness can coexist with late vagal hyper-reactivity [@besnier2017exercise], and aligns with the concept of autonomic resilience [@Enhancing2025Castillo].

>>>>

To model the RR interval (RRi) across a complete rest-exercise-recovery protocol, we implemented the coupled-logistic RRi-vs-time model proposed by Castillo-Aguilar et al. (2025) [@castillo2025enhancing]. Under this specification, each observed RRi is assumed to follow a normal distribution centered on a time-dependent function. This data generation process is depicted in @eq-data-generation-process.

@@

However, this vagal-centric profile was also characterized by a slower return to baseline heart rate after exercise. Despite a less pronounced initial increase in heart rate, individuals with more CD21^+^/CD11c^+^ B cells took longer to recover. This protracted recovery could stem from a less efficient re-establishment of autonomic balance following a moderated sympathetic response, where the sympathetic nervous system (SNS) might not have been sufficiently activated to trigger a strong subsequent vagal rebound. Alternatively, it might indicate a degree of autonomic rigidity [@castillo2025enhancing], where a predominantly parasympathetic system at rest exhibits difficulty in rapidly adjusting after a perturbation. The lower $c$ parameter (recovery proportion of the RRi curve) observed in this group supports the notion of reduced autonomic flexibility, suggesting that while a basal anti-inflammatory environment might be present, the capacity for rapid adaptation to acute physiological challenges could be limited.

@@

A notable and potentially beneficial finding was the excellent autonomic recovery (high $c$ parameter) observed in the CD21^-^/CD11c^-^ group despite their lower initial vagal tone. This suggests a compensatory and efficient vagal reactivation following the sympathetic surge, possibly mediated by baroreceptor and mechanoreceptor reflexes responding to the exercise-induced cardiovascular changes [@besnier2017exercise]. This efficient cholinergic recovery could aid in resolving immune activation once the exercise stimulus ceases. Thus, individuals with a more sympathicotonic profile might be capable of mounting strong but transient responses, followed by a relatively rapid return to autonomic balance mediated by the parasympathetic nervous system. This pattern resonates with descriptions of mild autonomic insufficiency, where sympathetic hyper-responsiveness can coexist with late vagal hyper-reactivity [@besnier2017exercise], and aligns with the concept of autonomic resilience [@castillo2025enhancing].
